### 2024-06-06 Scripts/Scripts-collection.Rmd
Update Scripts-collection.Rmd

df_profiles_vegan  <-  read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\microbial_profile-feasibility_validation.csv)",header = TRUE)
metadata = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\metadata-microbial_profile-feasibility_validation.csv)",header = TRUE)

@@

df_diversity  <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\alpha_diversity-comparison.csv)",header = TRUE)
df_diversity$Group  <- factor(df_diversity$Group,levels = c("Undepleted","Depleted"))

@@

df_total_args  <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\total_arg_abundance-comparison.csv)",header = TRUE)
df_total_args$Group  <- factor(df_total_args$Group,levels = c("Undepleted","Depleted"))
df_total_args$total_arg_abundance_log10 <- log10(df_total_args$total_arg_abundance)
my_comparisons <- list(c("Undepleted","Depleted"))
p_arg_abundance <- ggplot(df_total_args, aes(x=Group,y=total_arg_abundance_log10,fill=Group)) +
  stat_boxplot(geom = "errorbar",width=0.15)+
  geom_boxplot(size=0.5 ) + #theme_classic2() +
  geom_line(aes(group=Order),colour='Gray75', size=0.7)+
  geom_line(size=0.3) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
  scale_x_discrete(labels = c("Control","Treatment")) +
  stat_compare_means(paired = T,label.y = 1.8,comparisons = my_comparisons,label = "p.signif",size=7,bracket.size = 0.5) +
  stat_compare_means(paired = T,label.y = 2.5,label.x = 1,size=8) + 
  labs(x = NULL, y = "Total ARG abundance (log10)") +
  theme_pubr(base_size = 20, border =F,legend = "none")

@@

df_diversity  <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\alpha_diversity-metaphlan_speices-all_patients.csv)",header = TRUE)
df_metadata_all  <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\metaData.csv)",header = TRUE)

### merge the metadata and alpha diversity data

df_subset <- select(df_metadata_all, SampleID, Diagnosed.Pneumonia, Antibiotic.Use)

df_merged <- merge(df_diversity, df_subset, by = "SampleID")
df_merged_subset <- df_merged[df_merged$Diagnosed.Pneumonia %in% c("Yes", "No"), ]
df_merged_subset$Diagnosed.Pneumonia   <- factor(df_merged_subset$Diagnosed.Pneumonia,levels = c("No","Yes"))
my_comparisons <- list(c("No",'Yes'))

p_diversity_shannon <- ggplot(df_merged_subset, aes(x=Diagnosed.Pneumonia,y=Alpha_diversity_Shannon,fill=Diagnosed.Pneumonia)) +
  stat_boxplot(geom = "errorbar",width=0.15)+
  geom_boxplot(size=0.5 ) + #theme_classic2() +
  geom_line(size=0.3) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
  scale_x_discrete(labels = c("No Pneumonia","Pneumonia")) +
  stat_compare_means(label.y = 3.2,comparisons = my_comparisons,label = "p.signif",size=7,bracket.size = 0.5) +
  stat_compare_means(label.y = 3.8,label.x = 1,size=8) + 
  labs(x = NULL, y = "Alpha diversity (Shannon)") +
  theme_pubr(base_size = 21, border =F,legend = "none")
ggpar(p_diversity_shannon,x.text.angle = 30,legend = 'none')

>>>>

df_profiles_vegan  <-  read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\microbial_profile-feasibility_validation.csv)",header = TRUE) # save in the same file 'microbial_profile-feasibility_validation.txt'
metadata = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\metadata-microbial_profile-feasibility_validation.csv)",header = TRUE)  # save in the same file 'microbial_profile-feasibility_validation.txt'

@@

df_diversity  <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\alpha_diversity-feasibility_validation-comparison.csv)",header = TRUE)
df_diversity$Group  <- factor(df_diversity$Group,levels = c("Undepleted","Depleted"))

@@

df_total_args  <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\total_arg_abundance-feasibility_validation.csv)",header = TRUE)
df_total_args$Group  <- factor(df_total_args$Group,levels = c("Undepleted","Depleted"))
df_total_args$total_arg_abundance_log10 <- log10(df_total_args$total_arg_abundance)
my_comparisons <- list(c("Undepleted","Depleted"))
p_arg_abundance <- ggplot(df_total_args, aes(x=Group,y=total_arg_abundance_log10,fill=Group)) +
  stat_boxplot(geom = "errorbar",width=0.15)+
  geom_boxplot(size=0.5 ) + #theme_classic2() +
  geom_line(aes(group=Order),colour='Gray75', size=0.7)+
  geom_line(size=0.3) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
  scale_x_discrete(labels = c("Control","Treatment")) +
  stat_compare_means(paired = T,label.y = 1.8,comparisons = my_comparisons,label = "p.signif",size=7,bracket.size = 0.5) +
  stat_compare_means(paired = T,label.y = 2.5,label.x = 1,size=8) + 
  labs(x = NULL, y = "Total ARG abundance (log10)") +
  theme_pubr(base_size = 20, border =F,legend = "none")

@@

df_diversity  <- read.csv(r"(G:\Bio-Analysis\Python\Vscode\Task01-NEW\Data_submission\GitHub_repository\Data_repository\Supplementary_figures\alpha_diversity-comparison-pneumonia_vs_no_pneumonia.csv)",header = TRUE)
df_merged_subset$Diagnosed.Pneumonia   <- factor(df_merged_subset$Diagnosed.Pneumonia,levels = c("No","Yes"))

my_comparisons <- list(c("No",'Yes'))

p_diversity_shannon <- ggplot(df_merged_subset, aes(x=Diagnosed.Pneumonia,y=Alpha_diversity_Shannon,fill=Diagnosed.Pneumonia)) +
  stat_boxplot(geom = "errorbar",width=0.15)+
  geom_boxplot(size=0.5 ) + #theme_classic2() +
#   geom_line(aes(group=Order),colour='Gray75', size=0.7)+
  geom_line(size=0.3) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
  scale_x_discrete(labels = c("No Pneumonia","Pneumonia")) +
  stat_compare_means(label.y = 3.2,comparisons = my_comparisons,label = "p.signif",size=7,bracket.size = 0.5) +
  stat_compare_means(label.y = 3.8,label.x = 1,size=8) + 
  labs(x = NULL, y = "Alpha diversity (Shannon)") +
  theme_pubr(base_size = 21, border =F,legend = "none")

ggpar(p_diversity_shannon,x.text.angle = 30,legend = 'none')
